Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings

### 2021-02-08 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Many small tweaks

\documentclass[hideothersubsections, usenames,dvipsnames,11pt]{beamer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{curves}
\usepackage{epic}
\usepackage{epsfig}
\usepackage{fix-cm}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{mathpazo}
\usepackage{multimedia}
\usepackage{multicol}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{tikz}

@@

\begin{frame}
\frametitle{Business Practices of Small Firms}

	\citet{McKenzie2017} identify \textcolor{bdf}{set of XX best practices} most closely associated with business performance
	\begin{itemize_2pt}
		\item 5 major domains of business practices
		\begin{enumerate_2pt}
			\item Book-keeping and accounting
			\item ?
			\item ?
			\item Inventory management and stock control
			\item Marketing
		\end{enumerate_2pt}
	\item[] $\rightarrow$ Association with performance robust across industries and countries
	\item[] $\rightarrow$
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Business Practices of Small Firms}
	\citet{McKenzie2017} identify set of XX practices most closely associated with business performance
	\begin{itemize_2pt}
		\item Example practices:
		\begin{enumerate_2pt}
			\item e.g., 
			\item e.g., 
			\item e.g., 
			\item e.g., 
			\item e.g., 
		\end{enumerate_2pt}
	\end{itemize_2pt}

@@

\begin{frame}
\frametitle{History and Prevalence}
	\begin{itemize_2pt}
		\item At least \textcolor{bdf}{USD 1 billion per year} (to 4-5 million beneficiary entrepreneurs; \citet{McKenzie2020})
		\item Classical training programs \emph{precede} evidence that business practices vary and are predictive for productivity
		\item Examples:
		\begin{itemize_2pt}
			\item Start and Improve Your Business (ILO)
			\item Business Edge (IFC)
			\item EMPRETEC Entrepreneurship Training Workshop (UNCTAD)
		\end{itemize_2pt} 
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Typical Training Program}
	Content
	\begin{itemize_2pt}
	%\textcolor{}{}
	\item Training is delivered by 600 local certified trainers and by a pool of approximately 60 international master trainers. All trainers are also entrepreneurs.
	\item Empretec Training Workshops offer different levels of instruction that include:
	\item 6-day courses (48 hours); 32-hour (usually spread over 4 days) for micro-entrepreneurs with low levels of literacy; Interactive coaching based on real business challenges of participants.
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

	Including more recent evaluations \citep{McKenzie2020}

@@

	\begin{itemize_2pt}
		\item Targeting \textcolor{bdf}{specific subgroups} of the population
		\begin{itemize_2pt}
			\item Treating individuals with particular promise (e.g., high-growth firms)
			\item[] $\rightarrow$ \textcolor{bdf}{Maximizing impact} (or cost-effectiveness)
			\item Serving marginalized or disadvantaged groups
			\item[] $\rightarrow$ Alleviating \textcolor{bdf}{particularly severe constraints}
			\item[] $\rightarrow$ 
			\item \textcolor{bdf}{Maximizing statistical power} through homogeneity
		\end{itemize_2pt}

@@

@@

\begin{frame}
\frametitle{Heterogeneity of Impact}
	\begin{itemize_2pt}
	\item Heterogeneity of treatment effects poorly understood across different approaches
	\item Potential constraints are manifold, and likely context-dependent
	\item Some already mentioned in passing:
	\begin{itemize_2pt}
		\item Credit constraints \citep[see, e.g.,][]{} McKenzie cash paper
		\item Gender norms and constraints
		\item Age-related network and knowledge/skill constraints
	\end{itemize_2pt} 
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Family Commitments}
	\begin{itemize_2pt}
	\item 
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Identity Concerns}
	\begin{itemize_2pt}
	\item 
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Local Relevance of Best Practices}
	\begin{itemize_2pt}
	\item 
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

-----

@@

\begin{frame}[label=references, allowframebreaks]
\frametitle{References}
\bibliographystyle{econometrica}
\bibliography{SME_library}
\end{frame}

@@

\begin{frame}{Appendix Overview}
\tableofcontents[currentsection,hideothersubsections]
\end{frame}

>>>>

\documentclass[hideothersubsections, usenames,dvipsnames,11pt]{beamer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{curves}
\usepackage{epic}
\usepackage{epsfig}
\usepackage{fix-cm}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{mathpazo}
\usepackage{multimedia}
\usepackage{multicol}
\usepackage{natbib}
\usepackage{setspace}

@@

	\citet{McKenzie2017} identify \textcolor{bdf}{set of XX best practices} most closely associated with business performance
	\begin{itemize_2pt}
		\item 4 major domains of business practices
		\begin{enumerate_2pt}
			\item Book-keeping and accounting
			\item Financial planning
			\item Inventory management and stock control
			\item Marketing
		\end{enumerate_2pt}
	\item[] $\rightarrow$ Association with performance robust across industries and countries
	\item[] $\rightarrow$
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Business Practices in Small Firms}
	\citet{McKenzie2017} identify set of XX practices most closely associated with business performance
	\begin{itemize_2pt}
		\item Example practices:
		\begin{enumerate_2pt}
			\item e.g., 
			\item e.g., 
			\item e.g., 
			\item e.g.,  
		\end{enumerate_2pt}
	\end{itemize_2pt}

@@

\begin{frame}
\frametitle{History and Prevalence}
	\begin{itemize_2pt}
		\item At least \textcolor{bdf}{USD 1 billion per year} (to 4-5 million entrepreneurs; \citet{McKenzie2020})
		\item Classical training programs \emph{precede} evidence that business practices vary and are predictive for productivity

		\item Examples:
		\begin{itemize_2pt}
			\item Start and Improve Your Business (ILO)
			\item Business Edge (IFC)
			\item EMPRETEC Entrepreneurship Training Workshop (UNCTAD)
		\end{itemize_2pt} 
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Typical Training Program}
	Content
	\begin{itemize_2pt}
	%\textcolor{}{}
	\item \textcolor{red}{Training is delivered by 600 local certified trainers and by a pool of approximately 60 international master trainers. All trainers are also entrepreneurs.
	\item Empretec Training Workshops offer different levels of instruction that include:
	\item 6-day courses (48 hours); 32-hour (usually spread over 4 days) for micro-entrepreneurs with low levels of literacy; Interactive coaching based on real business challenges of participants.}
	\end{itemize_2pt}
\end{frame}

@@

	Including more recent evaluations \citep[see,][]{McKenzie2020}

@@

	\begin{itemize_2pt}
		\item Targeting \textcolor{bdf}{specific subgroups} of the population
		\begin{itemize_2pt}
			\item Alleviating \textcolor{bdf}{particularly severe constraints}
			\item[] $\rightarrow$ Marginalized or disadvantaged groups (e.g., women, youth)
			\item  Maximizing \textcolor{bdf}{treatment impact} (or cost-effectiveness) 
			\item[] $\rightarrow$ Promising entrepreneurs (e.g., high-growth firms)

			\item Plus: \textcolor{bdf}{Maximizing statistical power} through homogeneity
		\end{itemize_2pt}

@@

\begin{frame}
\frametitle{On-site Consulting}

	Consulting is intensive, tailored business advice
	\begin{itemize_2pt}
		\item Common interventions take 88 to 500 hours and more \citep{}
	\item[] $\rightarrow$ Typically 2-4 hours, between twice weekly and monthly
	\item Typical price point between \textcolor{red}{$USD$ 3,000 and 12,000 per firm} \citep{}
	\item One-on-one or group-based
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Heterogeneity of Impact}

Heterogeneity of treatment effects poorly understood across different approaches
\begin{itemize_2pt}
	\item Potential constraints are manifold, and likely context-dependent

	\item Some more obvious constraints (already mentioned in passing):
	\begin{itemize_2pt}
		\item \textcolor{bdf}{Credit constraints} \citep[see, e.g.,][]{} McKenzie cash paper
		\item \textcolor{bdf}{Gender norms and constraints}
		\item \textcolor{bdf}{Age-related} network and knowledge/skill \textcolor{bdf}{constraints}
	\end{itemize_2pt} 
\end{itemize_2pt}

$\rightarrow$ More recent literature highlights \textcolor{bdf}{behavioral constraints}

@@

\begin{frame}
\frametitle{Dynamic complementarities in skill acquisition}

Complementarities in skills
\begin{itemize_2pt}
	\item
\end{itemize_2pt}

Learning styles
\begin{itemize_2pt}
	\item
\end{itemize_2pt}

\begin{frame}
\frametitle{Family Commitments}
\begin{itemize_2pt}
	\item Interesting; \textcolor{red}{no beh const}
	\vspace{0.1in}
\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Segregated Markets}
\begin{itemize_2pt}
	\item Missing economies of scale
	\item \textcolor{red}{Interesting; not behavioral constraint}
	\vspace{0.1in}
\end{itemize_2pt}
\end{frame}

%\begin{frame}
%\frametitle{Identity Concerns}
%\begin{itemize_2pt}
%	\item 
%	\vspace{0.1in}
%\end{itemize_2pt}
%\end{frame}

@@

\begin{frame}
\frametitle{Local Relevance of Business Practices}
\begin{itemize_2pt}
	\item 
	\vspace{0.1in}
\end{itemize_2pt}
\end{frame}

@@

@@

\appendix
\begin{frame}[label=references, allowframebreaks]
\frametitle{References}
\bibliographystyle{econometrica}
\bibliography{SME_library}
\end{frame}

@@

%\begin{frame}{Appendix Overview}
%\tableofcontents[currentsection,hideothersubsections]
%\end{frame}
